---
title: "M3T3 - Evaluate Techniques for Wifi Locationing"
output: 
  html_notebook: 
    number_sections: yes
    theme: paper
---

Wi-Fi positioning system (WPS), is used when GPS can’t receive the signal. To improve the user experience, it exist the Wi-Fi Fingerprinting. That system consist of estimating the position of a user using a smartphone that sends a signal (the fingerprint or instance) that is recived by a Wireless Access Points (WAPs).  Two files "trainingData.csv" and "validationData.csv" will be used to solve this problem.

# Enviroment Setup
## Load Packages
```{r, echo=FALSE}
#-Load packages
library(dplyr)
library(ISLR)
library(lattice)
library(ggplot2)
library(caret)
library(ggmap)
library(caTools)
library(gridExtra)
library(ranger)
library(e1071)
library(readr)
library(tidyverse)  
library(kknn)        
library(kernlab)     
library(rgl)        
library(scatterplot3d) 
library(scales)     
library(ranger)     
library(C50)        
library(broom)       
library(kableExtra)  
library(knitr)
```
## Load Data

```{r}
#-Training Data
train <- read.csv("~/R/XTOL/Module3/Task3/trainingData.csv")
valid <- read.csv("~/R/XTOL/Module3/Task3/validationData.csv")
dim(train)
dim(valid)

# Attribute Definitions
wifi_defTable <- read.csv("~/R/XTOL/Module3/Task3/definition_table.csv")
  
#-Generate table of variable definitions
kable(wifi_defTable, caption = 'Attribute Definitions') %>%   kable_styling(bootstrap_options = c('striped', 'hover', 'responsive', 'bordered'), 
                full_width = F, 
                font_size = 14)
```

## Data Exploration

```{r}
summary(train[,510:529])
summary(valid[,510:529])

# Plot location with both data sets
plot(train$LONGITUDE, train$LATITUDE)
plot(valid$LONGITUDE, valid$LATITUDE)

#3D image of reference point locations in data set
scatterplot3d(train$LONGITUDE, train$LATITUDE, train$FLOOR,
              type='p',
              highlight.3d = FALSE,
              color='blue',
              angle=155,
              pch=16,
              box=FALSE,
              main = "Location Reference Points Across Three Buildings of UJIIndoorLoc Data Set",
              cex.lab = 1,
              cex.main=1,
              cex.sub=1,
              col.sub='blue',
              xlab='Longitude', ylab='Latitude',zlab = 'Building Floor') 

```

# Pre-processing

```{r}
#Merge both data. Divide full data
set.seed(100)
data <- rbind(train, valid)
sample <- sample.split(data, SplitRatio = .70)
training <- subset(data, sample ==TRUE)
validation <- subset(data, sample == FALSE)
```

## Separate data by building

```{r}
#Separate data by building in train & valid
build.0 <- filter(training, BUILDINGID == 0)
build.1 <- filter(training, BUILDINGID == 1)
build.2 <- filter(training, BUILDINGID == 2)

build.0.v <- filter(validation, BUILDINGID == 0)
build.1.v <- filter(validation, BUILDINGID == 1)
build.2.v <- filter(validation, BUILDINGID == 2)

#Create a data frame for each feature
#TRAIN
#Build 0
build.0.lat <- data.frame(build.0$LATITUDE, build.0[,1:520])
build.0.long <- data.frame(build.0$LONGITUDE, build.0[,1:520])
build.0.floor <- data.frame(build.0$FLOOR, build.0[,1:520])

#Build 1
build.1.lat <- data.frame(build.1$LATITUDE, build.1[,1:520])
build.1.long <- data.frame(build.1$LONGITUDE, build.1[,1:520])
build.1.floor <- data.frame(build.1$FLOOR, build.1[,1:520])

#Build 2
build.2.lat <- data.frame(build.2$LATITUDE, build.2[,1:520])
build.2.long <- data.frame(build.2$LONGITUDE, build.2[,1:520])
build.2.floor <- data.frame(build.2$FLOOR, build.2[,1:520])

#VALID
#Build 0
build.0.lat.v <- data.frame(build.0.v$LATITUDE, build.0.v[,1:520])
build.0.long.v <- data.frame(build.0.v$LONGITUDE, build.0.v[,1:520])
build.0.floor.v <- data.frame(build.0.v$FLOOR, build.0.v[,1:520])

#Build 1
build.1.lat.v <- data.frame(build.1.v$LATITUDE, build.1.v[,1:520])
build.1.long.v <- data.frame(build.1.v$LONGITUDE, build.1.v[,1:520])
build.1.floor.v <- data.frame(build.1.v$FLOOR, build.1.v[,1:520])

#Build 2
build.2.lat.v <- data.frame(build.2.v$LATITUDE, build.2.v[,1:520])
build.2.long.v <- data.frame(build.2.v$LONGITUDE, build.2.v[,1:520])
build.2.floor.v <- data.frame(build.2.v$FLOOR, build.2.v[,1:520])
```

## Data Sampling

```{r}
#Sample the data taking X random values
#TRAIN
#Build 0
sample.build.0.lat <- build.0.lat[sample(1:nrow(build.0.lat), 4000, replace = FALSE),]
sample.build.0.long <- build.0.long[sample(1:nrow(build.0.long), 4000, replace = FALSE),]
sample.build.0.floor <- build.0.floor[sample(1:nrow(build.0.floor), 4000, replace = FALSE),]
#Build 1
sample.build.1.lat <- build.1.lat[sample(1:nrow(build.1.lat), 3000, replace = FALSE),]
sample.build.1.long <- build.1.long[sample(1:nrow(build.1.long), 3000, replace = FALSE),]
sample.build.1.floor <- build.1.floor[sample(1:nrow(build.1.floor), 3000, replace = FALSE),]
#Build 2
sample.build.2.lat <- build.2.lat[sample(1:nrow(build.2.lat), 6000, replace = FALSE),]
sample.build.2.long <- build.2.long[sample(1:nrow(build.2.long), 6000, replace = FALSE),]
sample.build.2.floor <- build.2.floor[sample(1:nrow(build.2.floor), 6000, replace = FALSE),]

#Convert FLOOR fetaure in factor
sample.build.0.floor$build.0.FLOOR <- as.factor(sample.build.0.floor$build.0.FLOOR)
sample.build.1.floor$build.1.FLOOR <- as.factor(sample.build.1.floor$build.1.FLOOR)
sample.build.2.floor$build.2.FLOOR <- as.factor(sample.build.2.floor$build.2.FLOOR)
```

# Fiting Models

## KNN
### Building 0

```{r}
### Building 0 ###

# Train Control
trctrlKNN <- trainControl(method = "cv", number = 5, verboseIter = TRUE)
preProcessKNN <- c("zv", "medianImpute")

### Model Training ###
# Latitud #
knn.lat.0 <- train(build.0.LATITUDE ~ ., sample.build.0.lat, method = "knn", trControl = trctrlKNN, preProcess = preProcessKNN)

# Longitud #
knn.long.0 <- train(build.0.LONGITUDE ~ ., sample.build.0.long, method = "knn", trControl = trctrlKNN, preProcess = preProcessKNN)

# Floor #
knn.floor.0 <- train(build.0.FLOOR ~ ., sample.build.0.floor, method = "knn", trControl = trctrlKNN , preProcess = preProcessKNN)

### Prediction ###
# Latitud #
pred.knn.lat.0 <- predict(knn.lat.0, build.0.lat.v)

# Longitud #
pred.knn.long.0 <- predict(knn.long.0, build.0.long.v)

# Floor #
pred.knn.floor.0 <- predict(knn.floor.0, build.0.floor.v)

# Post Resample #
# Latitud #
PRKNNb0lat0 <- postResample(pred.knn.lat.0, build.0.lat.v$build.0.v.LATITUDE)
PRKNNb0lat0

# Longitud #
PRKNNb0lon0 <- postResample(pred.knn.long.0, build.0.long.v$build.0.v.LONGITUDE)
PRKNNb0lon0

# Accuracy #
conf.matrix.knn.floor.0 <- table(pred.knn.floor.0, build.0.floor.v$build.0.v.FLOOR)
accuracy.knn.floor.0 <- (sum(diag(conf.matrix.knn.floor.0))) / sum(conf.matrix.knn.floor.0)
accuracy.knn.floor.0 <- accuracy.knn.floor.0 * 100
accuracy.knn.floor.0

```

### Building 1

```{r}
### Building 1 ###
### Model Training ###
# Latitud #
knn.lat.1 <- train(build.1.LATITUDE ~ ., sample.build.1.lat, method = "knn", trControl = trctrlKNN, preProcess = preProcessKNN)

# Longitud #
knn.long.1 <- train(build.1.LONGITUDE ~ ., sample.build.1.long, method = "knn", trControl = trctrlKNN, preProcess = preProcessKNN)

# Floor #
knn.floor.1 <- train(build.1.FLOOR ~ ., sample.build.1.floor, method = "knn", trControl = trctrlKNN , preProcess = preProcessKNN)

### Prediction ###
# Latitud #
pred.knn.lat.1 <- predict(knn.lat.1, build.1.lat.v)

# Longitud #
pred.knn.long.1 <- predict(knn.long.1, build.1.long.v)

# Floor #
pred.knn.floor.1 <- predict(knn.floor.1, build.1.floor.v)

# Post Resample #
# Latitud #
PRKNNb0lat1 <- postResample(pred.knn.lat.1, build.1.lat.v$build.1.v.LATITUDE)
PRKNNb0lat1

# Longitud #
PRKNNb0lon1 <- postResample(pred.knn.long.1, build.1.long.v$build.1.v.LONGITUDE)
PRKNNb0lon1

# Accuracy #
conf.matrix.knn.floor.1 <- table(pred.knn.floor.1, build.1.floor.v$build.1.v.FLOOR)
accuracy.knn.floor.1 <- (sum(diag(conf.matrix.knn.floor.1))) / sum(conf.matrix.knn.floor.1)
accuracy.knn.floor.1 <- accuracy.knn.floor.1 * 100
accuracy.knn.floor.1
```

### Building 2

```{r}
### Building 2 ###
### Model Training ###
# Latitud #
knn.lat.2 <- train(build.2.LATITUDE ~ ., sample.build.2.lat, method = "knn", trControl = trctrlKNN, preProcess = preProcessKNN)

# Longitud #
knn.long.2 <- train(build.2.LONGITUDE ~ ., sample.build.2.long, method = "knn", trControl = trctrlKNN, preProcess = preProcessKNN)

# Floor #
knn.floor.2 <- train(build.2.FLOOR ~ ., sample.build.2.floor, method = "knn", trControl = trctrlKNN , preProcess = preProcessKNN)

### Prediction ###
# Latitud #
pred.knn.lat.2 <- predict(knn.lat.2, build.2.lat.v)

# Longitud #
pred.knn.long.2 <- predict(knn.long.2, build.2.long.v)

# Floor #
pred.knn.floor.2 <- predict(knn.floor.2, build.2.floor.v)

### Post Resample ###
# Latitud #
PRKNNb0lat2 <- postResample(pred.knn.lat.2, build.2.lat.v$build.2.v.LATITUDE)
PRKNNb0lat2

# Longitud #
PRKNNb0lon2 <- postResample(pred.knn.long.2, build.2.long.v$build.2.v.LONGITUDE)
PRKNNb0lon2

# Accuracy #
conf.matrix.knn.floor.2 <- table(pred.knn.floor.2, build.2.floor.v$build.2.v.FLOOR)
accuracy.knn.floor.2 <- (sum(diag(conf.matrix.knn.floor.2))) / sum(conf.matrix.knn.floor.2)
accuracy.knn.floor.2 <- accuracy.knn.floor.2 * 100
accuracy.knn.floor.2
```

### Save KNN Models

```{r}
# Building 0
saveKNN.lat.0 <- saveRDS(knn.lat.0, 'modelknn.lat.0.rds')
saveKNN.long.0 <- saveRDS(knn.long.0, 'modelknn.long.0.rds')
saveKNN.floor.0 <- saveRDS(knn.floor.0, 'modelknn.floor.0.rds')

# Building 1
saveKNN.lat.1 <- saveRDS(knn.lat.1, 'modelGknn.lat.1.rds')
saveKNN.long.1 <- saveRDS(knn.long.1, 'modelknn.long.1.rds')
saveKNN.floor.1 <- saveRDS(knn.floor.1, 'modelknn.floor.1.rds')

# Building 2
saveKNN.lat.2 <- saveRDS(knn.lat.2, 'modelknn.lat.2.rds')
saveKNN.long.2 <- saveRDS(knn.long.2, 'modelknn.long.2.rds')
saveKNN.floor.2 <- saveRDS(knn.floor.2, 'modelknn.floor.2.rds')
```

## Random Forest 
### Building 0

```{r}
# Train Control
trctrlRF <- trainControl(method = "cv", number = 5, verboseIter = TRUE)
preProcessRF <- c("zv", "medianImpute")
tunegridRF <- expand.grid(mtry=c(32))

### Building 0 ###
### Model Training ###
# Latitud #
rfor.lat.0 <- train(build.0.LATITUDE ~ ., sample.build.0.lat, method = "rf", tuneGrid= tunegridRF, trControl = trctrlRF, preProcess = preProcessRF)

# Longitud #
rfor.long.0 <- train(build.0.LONGITUDE ~ ., sample.build.0.long, method = "rf", tuneGrid= tunegridRF, trControl = trctrlRF, preProcess = preProcessRF)

# Floor #
rfor.floor.0 <- train(build.0.FLOOR ~ ., sample.build.0.floor, method = "rf", tuneGrid= tunegridRF, trControl = trctrlRF, preProcess = preProcessRF)

### Prediction ###
# Latitud #
pred.rfor.lat.0 <- predict(rfor.lat.0, build.0.lat.v)

# Longitud #
pred.rfor.long.0 <- predict(rfor.long.0, build.0.long.v)

# Floor #
pred.rfor.floor.0 <- predict(rfor.floor.0, build.0.floor.v)

### Post Resample ###
# Latitud #
PRRFb0lat0 <- postResample(pred.rfor.lat.0, build.0.lat.v$build.0.v.LATITUDE)
PRRFb0lat0

# Longitud #
PRRFb0lon0 <- postResample(pred.rfor.long.0, build.0.long.v$build.0.v.LONGITUDE)
PRRFb0lon0

### Accuracy ###
#Floor
conf.matrix.rfor.floor.0 <- table(pred.rfor.floor.0, build.0.floor.v$build.0.v.FLOOR)
accuracy.rfor.floor.0 <- (sum(diag(conf.matrix.rfor.floor.0))) / sum(conf.matrix.rfor.floor.0)
accuracy.rfor.floor.0 <- accuracy.rfor.floor.0 * 100
accuracy.rfor.floor.0
```

### Building 1

```{r}
### Building 1 ###
### Model Training ###
# Latitud #
rfor.lat.1 <- train(build.1.LATITUDE ~ ., sample.build.1.lat, method = "rf", tuneGrid= tunegridRF, trControl = trctrlRF, preProcess = preProcessRF)

# Longitud #
rfor.long.1 <- train(build.1.LONGITUDE ~ ., sample.build.1.long, method = "rf", tuneGrid= tunegridRF, trControl = trctrlRF, preProcess = preProcessRF)

# Floor #
rfor.floor.1 <- train(build.1.FLOOR ~ ., sample.build.1.floor, method = "rf", tuneGrid= tunegridRF, trControl = trctrlRF, preProcess = preProcessRF)

### Prediction ###
# Latitud #
pred.rfor.lat.1 <- predict(rfor.lat.1, build.1.lat.v)

# Longitud #
pred.rfor.long.1 <- predict(rfor.long.1, build.1.long.v)

# Floor #
pred.rfor.floor.1 <- predict(rfor.floor.1, build.1.floor.v)

### Post Resample ###
# Latitud #
PRRFb0lat1 <- postResample(pred.rfor.lat.1, build.1.lat.v$build.1.v.LATITUDE)
PRRFb0lat1

# Longitud #
PRRFb0lon1 <- postResample(pred.rfor.long.1, build.1.long.v$build.1.v.LONGITUDE)
PRRFb0lon1

### Accuracy ###
#Floor
conf.matrix.rfor.floor.1 <- table(pred.rfor.floor.1, build.1.floor.v$build.1.v.FLOOR)
accuracy.rfor.floor.1 <- (sum(diag(conf.matrix.rfor.floor.1))) / sum(conf.matrix.rfor.floor.1)
accuracy.rfor.floor.1 <- accuracy.rfor.floor.1 * 100
accuracy.rfor.floor.1
```

### Building 2

```{r}
### Building 2 ###
### Model Training ###
# Latitud #
rfor.lat.2 <- train(build.2.LATITUDE ~ ., sample.build.2.lat, method = "rf", tuneGrid= tunegridRF, trControl = trctrlRF, preProcess = preProcessRF)

# Longitud #
rfor.long.2 <- train(build.2.LONGITUDE ~ ., sample.build.2.long, method = "rf", tuneGrid= tunegridRF, trControl = trctrlRF, preProcess = preProcessRF)

# Floor #
rfor.floor.2 <- train(build.2.FLOOR ~ ., sample.build.2.floor, method = "rf", tuneGrid= tunegridRF, trControl = trctrlRF, preProcess = preProcessRF)

### Prediction ###
# Latitud #
pred.rfor.lat.2 <- predict(rfor.lat.2, build.2.lat.v)

# Longitud #
pred.rfor.long.2 <- predict(rfor.long.2, build.2.long.v)

# Floor #
pred.rfor.floor.2 <- predict(rfor.floor.2, build.2.floor.v)

### Post Resample ###
# Latitud #
PRRFb0lat2 <- postResample(pred.rfor.lat.2, build.2.lat.v$build.2.v.LATITUDE)
PRRFb0lat2

# Longitud #
PRRFb0lon2 <- postResample(pred.rfor.long.2, build.2.long.v$build.2.v.LONGITUDE)
PRRFb0lon2

### Accuracy ###
#Floor
conf.matrix.rfor.floor.2 <- table(pred.rfor.floor.2, build.2.floor.v$build.2.v.FLOOR)
accuracy.rfor.floor.2 <- (sum(diag(conf.matrix.rfor.floor.2))) / sum(conf.matrix.rfor.floor.2)
accuracy.rfor.floor.2 <- accuracy.rfor.floor.2 * 100
accuracy.rfor.floor.2

```

### Save Random Forest Model

```{r}
# Building 0
saverfor.lat.0 <- saveRDS(rfor.lat.0, 'modelrfor.lat.0.rds')
saverfor.long.0 <- saveRDS(rfor.long.0, 'modelrfor.long.0.rds')
saverfor.floor.0 <- saveRDS(rfor.floor.0, 'modelrfor.floor.0.rds')

# Building 1
saverfor.lat.1 <- saveRDS(rfor.lat.1, 'modelrfor.lat.1.rds')
saverfor.long.1 <- saveRDS(rfor.long.1, 'modelrfor.long.1.rds')
saverfor.floor.1 <- saveRDS(rfor.floor.1, 'modelrfor.floor.1.rds')

# Building 2
saverfor.lat.2 <- saveRDS(rfor.lat.2, 'modelrfor.lat.2.rds')
saverfor.long.2 <- saveRDS(rfor.long.2, 'modelrfor.long.2.rds')
saverfor.floor.2 <- saveRDS(rfor.floor.2, 'modelrfor.floor.2.rds')
```


### Confusion Matrix for Floor Accuracy

```{r}
#KNN
#Build 0
conf.matrix.knn.floor.0

#Build 1
conf.matrix.knn.floor.1

#Build 2
conf.matrix.knn.floor.2

# Random Forest
#Build 0
conf.matrix.rfor.floor.0

#Build 1
conf.matrix.rfor.floor.1

#Build 2
conf.matrix.rfor.floor.2

```
## Xtreme Gradient Boosting Tree
### Building 0

```{r}
# Train Control
trctrlGB <- trainControl(method = "cv", number = 5, verboseIter = TRUE)
preProcessGB <- c("zv", "medianImpute")

### Building 0 ###
### Model Training ###
# Latitud #
GB.lat.0 <- train(build.0.LATITUDE ~ ., sample.build.0.lat, method = "xgbTree", trControl = trctrlGB, preProcess = preProcessRF)

# Longitud #
GB.long.0 <- train(build.0.LONGITUDE ~ ., sample.build.0.long, method = "xgbTree", trControl = trctrlGB, preProcess = preProcessRF)

# Floor #
GB.floor.0 <- train(build.0.FLOOR ~ ., sample.build.0.floor, method = "xgbTree", trControl = trctrlGB, preProcess = preProcessRF)

### Prediction ###
# Latitud #
pred.GB.lat.0 <- predict(GB.lat.0, build.0.lat.v)

# Longitud #
pred.GB.long.0 <- predict(GB.long.0, build.0.long.v)

# Floor #
pred.GB.floor.0 <- predict(GB.floor.0, build.0.floor.v)

### Post Resample ###
# Latitud #
GBb0lat0 <- postResample(pred.GB.lat.0, build.0.lat.v$build.0.v.LATITUDE)
GBb0lat0

# Longitud #
GBb0lon0 <- postResample(pred.GB.long.0, build.0.long.v$build.0.v.LONGITUDE)
GBb0lon0

### Accuracy ###
#Floor
conf.matrix.GB.floor.0 <- table(pred.GB.floor.0, build.0.floor.v$build.0.v.FLOOR)
accuracy.GB.floor.0 <- (sum(diag(conf.matrix.GB.floor.0))) / sum(conf.matrix.GB.floor.0)
accuracy.GB.floor.0 <- accuracy.GB.floor.0 * 100
accuracy.GB.floor.0
```

### Building 1

```{r}
### Building 1 ###
### Model Training ###
# Latitud #
GB.lat.1 <- train(build.1.LATITUDE ~ ., sample.build.1.lat, method = "xgbTree", trControl = trctrlGB, preProcess = preProcessRF)

# Longitud #
GB.long.1 <- train(build.1.LONGITUDE ~ ., sample.build.1.long, method = "xgbTree", trControl = trctrlGB, preProcess = preProcessRF)

# Floor #
GB.floor.1 <- train(build.1.FLOOR ~ ., sample.build.1.floor, method = "xgbTree", trControl = trctrlGB, preProcess = preProcessRF)

### Prediction ###
# Latitud #
pred.GB.lat.1 <- predict(GB.lat.1, build.1.lat.v)

# Longitud #
pred.GB.long.1 <- predict(GB.long.1, build.1.long.v)

# Floor #
pred.GB.floor.1 <- predict(GB.floor.1, build.1.floor.v)

### Post Resample ###
# Latitud #
GBb0lat1 <- postResample(pred.GB.lat.1, build.1.lat.v$build.1.v.LATITUDE)
GBb0lat1

# Longitud #
GBb0lon1 <- postResample(pred.GB.long.1, build.1.long.v$build.1.v.LONGITUDE)
GBb0lon1

### Accuracy ###
#Floor
conf.matrix.GB.floor.1 <- table(pred.GB.floor.1, build.1.floor.v$build.1.v.FLOOR)
accuracy.GB.floor.1 <- (sum(diag(conf.matrix.GB.floor.1))) / sum(conf.matrix.GB.floor.1)
accuracy.GB.floor.1 <- accuracy.GB.floor.1 * 100
accuracy.GB.floor.1
```

### Building 2

```{r}
### Building 2 ###
### Model Training ###
# Latitud #
GB.lat.2 <- train(build.2.LATITUDE ~ ., sample.build.2.lat, method = "xgbTree", trControl = trctrlGB, preProcess = preProcessRF)

# Longitud #
GB.long.2 <- train(build.2.LONGITUDE ~ ., sample.build.2.long, method = "xgbTree", trControl = trctrlGB, preProcess = preProcessRF)

# Floor #
GB.floor.2 <- train(build.2.FLOOR ~ ., sample.build.2.floor, method = "xgbTree", trControl = trctrlGB, preProcess = preProcessRF)

### Prediction ###
# Latitud #
pred.GB.lat.2 <- predict(GB.lat.2, build.2.lat.v)

# Longitud #
pred.GB.long.2 <- predict(GB.long.2, build.2.long.v)

# Floor #
pred.GB.floor.2 <- predict(GB.floor.2, build.2.floor.v)

### Post Resample ###
# Latitud #
GBb0lat2 <- postResample(pred.GB.lat.2, build.2.lat.v$build.2.v.LATITUDE)
GBb0lat2

# Longitud #
GBb0lon2 <- postResample(pred.GB.long.2, build.2.long.v$build.2.v.LONGITUDE)
GBb0lon2

### Accuracy ###
#Floor
conf.matrix.GB.floor.2 <- table(pred.GB.floor.2, build.2.floor.v$build.2.v.FLOOR)
accuracy.GB.floor.2 <- (sum(diag(conf.matrix.GB.floor.2))) / sum(conf.matrix.GB.floor.2)
accuracy.GB.floor.2 <- accuracy.GB.floor.2 * 100
accuracy.GB.floor.2
```
### save XGB Models

```{r}
# Building 0
saveGB.lat.0 <- saveRDS(GB.lat.0, 'modelGB.lat.0.rds')
saveGB.long.0 <- saveRDS(GB.long.0, 'modelGB.long.0.rds')
saveGB.floor.0 <- saveRDS(GB.floor.0, 'modelGB.floor.0.rds')

# Building 1
saveGB.lat.1 <- saveRDS(GB.lat.1, 'modelGB.lat.1.rds')
saveGB.long.1 <- saveRDS(GB.long.1, 'modelGB.long.1.rds')
saveGB.floor.1 <- saveRDS(GB.floor.1, 'modelGB.floor.1.rds')

# Building 2
saveGB.lat.2 <- saveRDS(GB.lat.2, 'modelGB.lat.2.rds')
saveGB.long.2 <- saveRDS(GB.long.2, 'modelGB.long.2.rds')
saveGB.floor.2 <- saveRDS(GB.floor.2, 'modelGB.floor.2.rds')
```

# Fit the Final Model
## Random Forest Model

```{r}
# Based on the previous results, the Random Forest Model is the most accurate model.
# Create Data Frame
lat <- data.frame(training$LATITUDE, training[,1:520])
long <- data.frame(training$LONGITUDE, training[,1:520])
floor <- data.frame(training$FLOOR, training[,1:520])

floor$training.FLOOR <- as.factor(floor$training.FLOOR)

lat.v <- data.frame(validation$LATITUDE, validation[,1:520])
long.v <- data.frame(validation$LONGITUDE, validation[,1:520])
floor.v <- data.frame(validation$FLOOR, validation[,1:520])

### Model Training ### 
# Train Control
trctrlRF <- trainControl(method = "cv", number = 5, verboseIter = TRUE)
preProcessRF <- c("zv", "medianImpute")
tunegridRF <- expand.grid(mtry=c(32))

# Latitud #
latitudeRF <- train(training.LATITUDE ~ ., lat, method = "rf", tuneGrid= tunegridRF, trControl = trctrlRF, preProcess = preProcessRF)

# Longitud #
longtitudeRF <- train(training.LONGITUDE ~ ., long, method = "rf", tuneGrid= tunegridRF, trControl = trctrlRF, preProcess = preProcessRF)

# Floor #
floorRF <- train(training.FLOOR ~ ., floor, method = "rf", tuneGrid= tunegridRF, trControl = trctrlRF, preProcess = preProcessRF)

### Prediction ###
# Latitud #
predictionlatRF <- predict(latitudeRF, lat.v)

# Longitud #
predictionlongRF <- predict(longtitudeRF, long.v)

# Floor #
predictionfloorRF <- predict(floorRF, floor.v)

### Post Resample ###
# Latitud #
postrsamplelatRF <- postResample(predictionlatRF, lat.v$validation.LATITUDE)
postrsamplelatRF

# Longitud #
postresamplelongRF <- postResample(predictionlongRF, long.v$validation.LONGITUDE)
postresamplelongRF

### Accuracy ###
#Floor
conf.matrix.rfor.floor <- table(predictionfloorRF, floor.v$validation.FLOOR)
accuracy.rfor.floor <- (sum(diag(conf.matrix.rfor.floor))) / sum(conf.matrix.rfor.floor)
accuracy.rfor.floor <- accuracy.rfor.floor * 100
accuracy.rfor.floor
conf.matrix.rfor.floor
```

## Relative Position Identification

```{r}
# RELATIVEPOSITION range: 1 - Inside, 2 - Outside in Front of the door

summary(build.0$RELATIVEPOSITION)
summary(build.1$RELATIVEPOSITION)
summary(build.2$RELATIVEPOSITION)
```

### Save Final Model

```{r}
# Final Model
save.latitudeRF <- saveRDS(latitudeRF, 'model.latitudeRF.rds')
saver.longtitudeRF <- saveRDS(longtitudeRF, 'model.longtitudeRF.rds')
saver.floorRF <- saveRDS(floorRF, 'model.floorRF.rds')
```

# Results Discussion 

The goal of this project was accomplished, the feasibility to determine / predict the location of a user based on WAPs signals, was successfully achieved.  
The predictions of the models are very accurate and quite representative. However, we have to take into account that we combined both datasets (Training and Validation) to create the models, since the training data had a lack of representativity. Hence, it is difficult to gauge if our model can have a problem of overfitting.
This model it’s an accurate and inexpensive way to determine an user location in indoor spaces, several use cases can be developed to take advantage of the model.

# Recomendations

Use the model RF to conduct the predictions since the R-squared values were the highest one and RMSE was the lowest one.
