---
title: "M4T3 - Develop Models - Galaxy"
output: 
  html_notebook: 
    number_sections: yes
    theme: journal
---

# Project Summary 
We will develop several models and pick the best model using Small matrix dataset which are manually labeled with a sentiment rating for iPhone. We will then use the best model to predict sentiment ratings of the large matrix dataset for iPhone.

# Enviroment Setup
This section contains the enviroment setup and data import steps.

```{r}
setwd("~/XTOL Big Data/Module 4/Task 3 - Develop Models/Iphone Analysis")

################
# Load packages
################
library(caret)
library(corrplot)
library(readr)
library(e1071)
library(C50)
library(kknn)
library(gbm)
library(dplyr)

#####################
# Parallel processing
#####################

library(doParallel) 

# Check number of cores and workers available 
detectCores()
cl <- makeCluster(4)
registerDoParallel(cl)
getDoParWorkers()

```

## Import Data

```{r}
###############
# Import data
##############

## Load training and test set
iphone_smallmatrix<- read.csv("~/XTOL Big Data/Module 4/Task 3 - Develop Models/Iphone Analysis/iphone_smallmatrix_labeled_8d.csv", stringsAsFactors = FALSE, header=T)
iphone_largematrix<- read.csv("~/XTOL Big Data/Module 4/Task 3 - Develop Models/Iphone Analysis/iphoneLargematrix.csv", stringsAsFactors = FALSE, header=T)

################
# Evaluate data
################

#--- Training Set ---#
summary(iphone_smallmatrix) 
str(iphone_smallmatrix) 
head(iphone_smallmatrix)
tail(iphone_smallmatrix)
table(iphone_smallmatrix$iphonesentiment)

# check for missing values 
is.na(iphone_smallmatrix)
any(is.na(iphone_smallmatrix))

# plot
hist(iphone_smallmatrix$iphonesentiment)
qqnorm(iphone_smallmatrix$iphonesentiment)  

#--- Prediction Set ---# 
summary(iphone_largematrix) 
str(iphone_largematrix) 
head(iphone_largematrix)
tail(iphone_largematrix)

# check for missing values 
is.na(iphone_largematrix)
any(is.na(iphone_largematrix))

```

# Pre-processing

```{r}
#############
# Preprocess
#############

#--- Training and test set ---#

# change variable types
iphone_smallmatrix$iphonesentiment <- as.factor(iphone_smallmatrix$iphonesentiment)
# normalize
preprocessParamsg <- preProcess(iphone_smallmatrix[,1:58], method = c("center", "scale"))
print(preprocessParamsg)
iphone_smallmatrix_N <- predict(preprocessParamsg, iphone_smallmatrix)
str(iphone_smallmatrix_N)

#--- Prediction set ---#

# drop ID variable
iphone_largematrix$id<- NULL
# Add a variable
iphone_largematrix$iphonesentiment <- as.factor(iphone_largematrix$iphonesentiment)
# normalize
iphone_largematrix_N <- predict(preprocessParamsg, iphone_largematrix)
str(iphone_largematrix_N)

##################
# Train/test sets
##################

# set random seed
set.seed(123)
# create the training partition that is 70% of total obs
inTrainingg <- createDataPartition(iphone_smallmatrix_N$iphonesentiment, p=0.7, list=FALSE)
# create training/testing dataset
gtrainSetN <- iphone_smallmatrix_N[inTrainingg,]   
gtestSetN <- iphone_smallmatrix_N[-inTrainingg,]   

# verify number of obs 
nrow(gtrainSetN)
nrow(gtestSetN)

################
# Train control
################

# set 5 fold cross validation
fitControl <- trainControl(method = "cv", number = 5)

```
# Train Models

Five algorithms will be tested to determine the best fit in terms of Kappa and accuracy.

## Decision Tree C5.0 Model

```{r}
## ------- Decision Tree C5.0 ------- ##
# set random seed
set.seed(123)
# train/fit
C5.0_Fitg <- train(iphonesentiment~., data=gtrainSetN, method="C5.0", trControl=fitControl, metric = "Kappa", tuneLength=5)
C5.0_Fitg

### Save model ###

saveRDS(C5.0_Fitg, "C5.0_Fitg.rds")
C5.0_Fitg <- readRDS("C5.0_Fitg.rds")

### C5.0 Prediction ###

# predict with C5.0
C5.0_Predg <- predict(C5.0_Fitg, gtestSetN)
C5.0_Predg 

#summarize predictions
summary(C5.0_Predg)

# performance measurement
postResample(C5.0_Predg, gtestSetN$iphonesentiment)

# plot
plot(C5.0_Predg,gtestSetN$iphonesentiment)

#calculate confusion Matrix
options(max.print=10000)
gcmC5.0 <-confusionMatrix(C5.0_Predg,gtestSetN$iphonesentiment, mode="everything")
gcmC5.0 
```

## Random Forest Model

```{r}
## ------- random forest ------- ##

# set random seed
set.seed(123)
# train/fit
rf_Fitg <- train(iphonesentiment~., data=gtrainSetN, method="rf", trControl=fitControl, metric = "Kappa",tuneLength=5) 
rf_Fitg

# Save the Model #
saveRDS(rf_Fitg, "rf_Fitg.rds")  
# load and name model
rf_Fitg <- readRDS("rf_Fitg.rds")

#---Predict testSet with  rf---#
# predict with rf
rf_Predg <- predict(rf_Fitg, gtestSetN)
rf_Predg 

#summarize predictions
summary(rf_Predg)

# performance measurement
postResample(rf_Predg, gtestSetN$iphonesentiment)

# plot
plot(rf_Predg,gtestSetN$iphonesentiment)

#calculate confusion Matrix
cmrfg <-confusionMatrix(rf_Predg,gtestSetN$iphonesentiment, mode="everything")
cmrfg

```

## SVM Model

```{r}
## ------- SVM ------- ##

# set random seed
set.seed(123)
# SVM train/fit
svm_Fitg <- train(iphonesentiment~., data=gtrainSetN, method="svmLinear", trControl=fitControl, metric = "Kappa",tuneLength=5) 
svm_Fitg

# Save SVM Model #
saveRDS(svm_Fitg, "svmFitg.rds")  

# load and name model
svm_Fitg<- readRDS("svmFitg.rds")

#---Predict testSet with  svm---#
# predict with svm
svm_Predg <- predict(svm_Fitg, gtestSetN)
svm_Predg 

#summarize predictions
summary(svm_Predg)

# performance measurement
postResample(svm_Predg, gtestSetN$iphonesentiment)

# plot
plot(svm_Predg,gtestSetN$iphonesentiment)

#calculate confusion Matrix
cmsvm <-confusionMatrix(rf_Predg,gtestSetN$iphonesentiment, mode="everything")
cmsvm

```

## KKNN Model

```{r}
## ------- KKNN------- ##

# set random seed
set.seed(123)

# KKNN train/fit
kknn_Fitg <- train(iphonesentiment~., data=gtrainSetN, method="kknn", trControl=fitControl, metric = "Kappa",tuneLength=5) 
kknn_Fitg

# Save the Model #
saveRDS(kknn_Fitg, "kknnFitg.rds")  

# load and name model
kknn_Fitg<- readRDS("kknnFitg.rds")

#---Predict testSet with kknn---#

# predict with kknn
kknnPredg <- predict(kknn_Fitg, gtestSetN)
# print predictions
kknnPredg

#summarize predictions
summary(kknnPredg)

#performance measurement
postResample(kknnPredg, gtestSetN$iphonesentiment)

# plot
plot(kknnPredg,gtestSetN$iphonesentiment)

#calculate confusion Matrix
cmkknng <-confusionMatrix(kknnPredg, gtestSetN$iphonesentiment)
cmkknng
```

## GBM Model

```{r}
## ------- GBM------- ##

#recode variable of training set
gtrainSetNG <-gtrainSetN
gtrainSetNG$iphonesentiment <- recode(gtrainSetN$iphonesentiment, '0' = 'seg0', '1' = 'seg1', '2' = 'seg2', '3' = 'seg3', '4' = 'seg4', '5' = 'seg5')
str(gtrainSetNG)

#recode variable of test set
gtestSetNG <-gtestSetN
gtestSetNG$iphonesentiment <- recode(gtestSetNG$iphonesentiment, '0' = 'seg0', '1' = 'seg1', '2' = 'seg2', '3' = 'seg3', '4' = 'seg4', '5' = 'seg5')
str(gtestSetNG)

# set random seed
set.seed(123)
# GBM train/fit
gmodel3<- train(iphonesentiment~., data=gtrainSetNG,method='gbm',trControl = fitControl,verbose=F,tuneLength=3)
gmodel3

# Save the Model #

saveRDS(gmodel3, "gbmFit3g.rds")  

# load and name model
gbm_Fit3g<- readRDS("gbmFit3g.rds")

#---Predict testSet---#

# predict with gbm
gbmPred1g <- predict(gbm_Fit3g, gtestSetNG)

# print predictions
gbmPred1g

# summarize predictions
summary(gbmPred1g)

# performance measurement
postResample(gbmPred1g, gtestSetNG$iphonesentiment)

# plot
plot(gbmPred1g,gtestSetN$iphonesentiment)

#calculate confusion Matrix
cmgbmg <-confusionMatrix(gbmPred1g, gtestSetNG$iphonesentiment, mode="everything")
cmgbmg

```

# Metrics Comparison

Find the best combination of data set and algorithm as measured by resulting performance metrics

```{r}
ModelFitResultsg <- resamples(list(C5.0=C5.0_Fitg,rf=rf_Fitg,SVM=svm_Fitg,kknn=kknn_Fitg,gbm=gbm_Fit3g))
# output summary metrics for tuned models 
summary(ModelFitResultsg)
```

# Feature Selection
You will then model with each of these new data sets to determine which method, if any, provides the best model accuracy for this project.

## Method 1 - Correlation

```{r}
#####################################
# RF Model - Method 1 - Correlation #
#####################################

options(max.print=1000000)
iphoneCOR <- iphone_smallmatrix_N
corrAll <- cor(iphoneCOR[,1:58])
corrAll 

# plot correlation matrix
corrplot(corrAll, order = "hclust")
corrplot(corrAll, method = "circle")
gcorr58<- cor(iphoneCOR[,1:58])

# create object with indexes of highly corr features
gcorrIVhigh <- findCorrelation(gcorr58, cutoff=0.8)

# print indexes of highly correlated attributes
gcorrIVhigh

# get var name of high corr IV
colnames(iphoneCOR[c(29)])
colnames(iphoneCOR[c(44)])
colnames(iphoneCOR[c(24)]) 
colnames(iphoneCOR[c(32)])
colnames(iphoneCOR[c(56)]) 
colnames(iphoneCOR[c(54)]) 
colnames(iphoneCOR[c(34)]) 
colnames(iphoneCOR[c(19)])
colnames(iphoneCOR[c(42)]) 
colnames(iphoneCOR[c(21)]) 
colnames(iphoneCOR[c(31)])
colnames(iphoneCOR[c(26)]) 
colnames(iphoneCOR[c(51)])
colnames(iphoneCOR[c(11)]) 
colnames(iphoneCOR[c(36)]) 
colnames(iphoneCOR[c(46)]) 
colnames(iphoneCOR[c(16)]) 
colnames(iphoneCOR[c(28)]) 
colnames(iphoneCOR[c(23)]) 
colnames(iphoneCOR[c(40)])
colnames(iphoneCOR[c(57)])
colnames(iphoneCOR[c(55)])
colnames(iphoneCOR[c(30)])
colnames(iphoneCOR[c(6)]) 
colnames(iphoneCOR[c(5)]) 

#################
# Feature removal
#################

# remove based on Feature Engineering (FE)
# create 34v ds
iphoneCOR34v<- iphoneCOR
iphoneCOR34v$samsungdisneg <- NULL
iphoneCOR34v$samsungperneg<- NULL
iphoneCOR34v$samsungdispos <- NULL
iphoneCOR34v$htcdisneg<- NULL
iphoneCOR34v$googleperneg<- NULL
iphoneCOR34v$googleperpos <- NULL
iphoneCOR34v$samsungdisunc <- NULL
iphoneCOR34v$samsungcamunc <- NULL
iphoneCOR34v$htcperpos <- NULL
iphoneCOR34v$nokiacamunc <- NULL
iphoneCOR34v$nokiadisneg <- NULL
iphoneCOR34v$nokiadispos <- NULL
iphoneCOR34v$nokiaperunc <- NULL
iphoneCOR34v$nokiacampos <- NULL
iphoneCOR34v$nokiadisunc <- NULL
iphoneCOR34v$nokiaperneg <- NULL
iphoneCOR34v$nokiacamneg <- NULL
iphoneCOR34v$iphonedisneg <- NULL
iphoneCOR34v$iphonedispos <- NULL
iphoneCOR34v$sonyperpos <- NULL
iphoneCOR34v$iosperunc <- NULL
iphoneCOR34v$sonydisneg <- NULL
iphoneCOR34v$iosperneg <- NULL
iphoneCOR34v$ios <- NULL
iphoneCOR34v$htcphone <- NULL
str(iphoneCOR34v)    

##################
# Train/test sets
##################
# set random seed
set.seed(123)

# create the training partition 70% of total obs
ginTrainingCOR <- createDataPartition(iphoneCOR34v$iphonesentiment, p=0.7, list=FALSE)

# create training/testing dataset
gtrainSetCOR <- iphoneCOR34v[ginTrainingCOR,]   
gtestSetCOR <- iphoneCOR34v[-ginTrainingCOR,]   

# verify number of obs 
nrow(gtrainSetCOR)
nrow(gtestSetCOR)

################
# Train control
################

# set 5 fold cross validation
fitControl <- trainControl(method = "cv", number = 5)

# train/fit

set.seed(123)
rf_FitCORg <- train(iphonesentiment~., data=gtrainSetCOR, method="rf", trControl=fitControl, metric = "Kappa",tuneLength=5) 
rf_FitCORg

# Save the model
saveRDS(rf_FitCORg, "rf_FitCORg.rds")  

# load and name model
rf_FitCORg <- readRDS("rf_FitCORg.rds")

#################
# Predict testSet
#################

# predict with rf
rf_Pred2g <- predict(rf_FitCORg, gtestSetCOR)
rf_Pred2g

# summarize predictions
summary(rf_Pred2g)

# performance measurement
postResample(rf_Pred2g, gtestSetCOR$iphonesentiment)
 

# calculate confusion Matrix
cmrfgcor <-confusionMatrix(rf_Pred2g,gtestSetCOR$iphonesentiment)
cmrfgcor
```

## Method 2 - Feature Variance

```{r}
##########################################
# RF Model - Method 2 - Feature Variance #
##########################################

#nearZeroVar() with saveMetrics = TRUE returns an object containing a table including: frequency ratio, percentage unique, zero variance and near zero variance 

gnzvMetrics <- nearZeroVar(iphone_smallmatrix_N, saveMetrics = TRUE)
gnzvMetrics


# nearZeroVar() with saveMetrics = FALSE returns an vector 
gnzv <- nearZeroVar(iphone_smallmatrix_N, saveMetrics = FALSE) 
gnzv

# create a new data set and remove near zero variance features
iphoneNZV <- iphone_smallmatrix_N[,-gnzv]
str(iphoneNZV)

##################
# Train/test sets
##################
# set random seed
set.seed(123)

# create the training partition 70 % of total obs
ginTrainingNZV <- createDataPartition(iphoneNZV$iphonesentiment, p=0.7, list=FALSE)

# create training/testing dataset
gtrainSetNZV <- iphoneNZV[ginTrainingNZV,]   
gtestSetNZV <- iphoneNZV[-ginTrainingNZV,]   

# verify number of obs 
nrow(gtrainSetNZV)
nrow(gtestSetNZV)

################
# Train control
################

# set 5 fold cross validation
fitControl <- trainControl(method = "cv", number = 5)

# train/fit
set.seed(123)
grf_FitNZV <- train(iphonesentiment~., data=gtrainSetNZV, method="rf", trControl=fitControl, metric = "Kappa",tuneLength=5) 
grf_FitNZV

# Save the Model #
saveRDS(grf_FitNZV, "grf_FitNZV.rds")  

# load and name model
grf_FitNZV<- readRDS("grf_FitNZV.rds")

#################
# Predict testSet
#################
# predict with rf
rf_Pred3g <- predict(grf_FitNZV, gtestSetNZV)
rf_Pred3g 
# summarize predictions
summary(rf_Pred3g)
# performance measurement
postResample(rf_Pred3g, gtestSetNZV$iphonesentiment)

# calculate confusion Matrix
cmrfgnzv <-confusionMatrix(rf_Pred3g,gtestSetNZV$iphonesentiment)
cmrfgnzv
```

## Method 3 - Feature Elimination

```{r}
#############################################
# RF Model - Method 3 - Feature Elimination #
#############################################

# Let's sample the data before using RFE
set.seed(123)
iphoneSample <- iphone_smallmatrix_N[sample(1:nrow(iphone_smallmatrix_N), 1000, replace=FALSE),]

# Set up rfeControl with randomforest, repeated cross validation and no updates
ctrl <- rfeControl(functions = rfFuncs, 
                   method = "cv",
                   repeats = 5,
                   verbose = FALSE)

# Use rfe and omit the response variable (attribute 59 iphonesentiment) 
rfeResultsg <- rfe(iphoneSample[,1:58], 
                  iphoneSample$iphonesentiment, 
                  sizes=(1:58), 
                  rfeControl=ctrl)

# Get results
rfeResultsg

# Save the Model
saveRDS(rfeResultsg, "rfeResultsg.rds")  

# load and name model
rfeResultsg<- readRDS("rfeResultsg.rds")

# Plot results
plot(rfeResultsg, type=c("g", "o"))

# create new data set with rfe recommended features
iphoneRFE <- iphone_smallmatrix_N[,predictors(rfeResultsg)]

# add the dependent variable to iphoneRFE
iphoneRFE$iphonesentiment <- iphone_smallmatrix_N$iphonesentiment
str(iphoneRFE)
head(iphone_smallmatrix_N)

# review outcome
str(iphoneRFE)
summary(iphoneRFE)

##################
# Train/test sets
##################

# set random seed
set.seed(123)

# create the training partition 70 % of total obs
ginTrainingRFE <- createDataPartition(iphoneRFE$iphonesentiment, p=0.7, list=FALSE)

# create training/testing dataset
gtrainSetRFE <- iphoneRFE[ginTrainingRFE,]   
gtestSetRFE <- iphoneRFE[-ginTrainingRFE,]   

# verify number of obs 
nrow(gtrainSetRFE)
nrow(gtestSetRFE)

################
# Train control
################

# set 5 fold cross validation
fitControl <- trainControl(method = "cv", number = 5)

# train/fit
set.seed(123)
rf_FitRFEg <- train(iphonesentiment~., data=gtrainSetRFE, method="rf", trControl=fitControl, metric = "Kappa",tuneLength=5) 
rf_FitRFEg

# Save the model
saveRDS(rf_FitRFEg, "rf_FitRFEg.rds")  

# load and name model
rf_FitRFEg <- readRDS("rf_FitRFEg.rds")

#################
# Predict testSet
#################
# predict with rf
rf_Pred5g <- predict(rf_FitRFEg, gtestSetRFE)
rf_Pred5g

# summarize predictions
summary(rf_Pred5g)

# performance measurement
postResample(rf_Pred5g, gtestSetRFE$iphonesentiment)

# calculate confusion Matrix
cmrfeg <-confusionMatrix(rf_Pred5g,gtestSetRFE$iphonesentiment)
cmrfeg
```

# Feature Engineering

Feature engineering is the art of working with the data so that it can more readily be consumed by machine learning algorithms. Feature engineering includes mutating existing attributes, combining attributes, deconstructing attributes and much more. 

In this step we will consider two possibilities:

A- Altering the dependant variable
B- Principal Component Analysis 

## Engineering the Dependant variable

From the previous step you probably saw that several of the dependant variable's factor levels had very poor Sensitivity and Balanced Accuracy. Do we really need 6 levels to understand positive and negative sentiment? Perhaps combining some of these levels will help increase accuracy and kappa. What if we remapped the values as follows:

1: negative
2: somewhat negative
3: somewhat positive
4: positive

```{r}
############################################################
# RF Model with RFE and Engineering the Dependant variable #
############################################################
# create a new dataset that will be used for recoding sentiment
iphoneRC <- iphoneRFE
# recode sentiment to combine factor levels 0 & 1 and 4 & 5
iphoneRC$iphonesentiment <- recode(iphoneRFE$iphonesentiment, '0' = 1, '1' = 1, '2' = 2, '3' = 3, '4' = 4, '5' = 4) 
# inspect results
summary(iphoneRC)
str(iphoneRC)
# make iphonesentiment a factor
iphoneRC$iphonesentiment <- as.factor(iphoneRC$iphonesentiment)

##################
# Train/test sets
##################

# set random seed
set.seed(123)
ginTrainingRC <- createDataPartition(iphoneRC$iphonesentiment, p=0.7, list=FALSE)
# create training/testing dataset
gtrainSetRC <- iphoneRC[ginTrainingRC,]   
gtestSetRC <- iphoneRC[-ginTrainingRC,]   

# verify number of obs 
nrow(gtrainSetRC)
nrow(gtestSetRC)

################
# Train control
################

# set 5 fold cross validation
fitControl <- trainControl(method = "cv", number = 5)

# train/fit

set.seed(123)
rf_FitRCg <- train(iphonesentiment~., data=gtrainSetRC, method="rf", trControl=fitControl, metric = "Kappa",tuneLength=5) 
rf_FitRCg

# Save the model
saveRDS(rf_FitRCg, "rf_FitRCg.rds")  

# load and name model
rf_FitRCg <- readRDS("rf_FitRCg.rds")

#################
# Predict testSet
#################
# predict with rf
rf_Pred6g <- predict(rf_FitRCg, gtestSetRC)
rf_Pred6g

# summarize predictions
summary(rf_Pred6g)

# performance measurement
postResample(rf_Pred6g, gtestSetRC$iphonesentiment)

# calculate confusion Matrix
cmrcg <-confusionMatrix(rf_Pred6g, gtestSetRC$iphonesentiment, mode="everything")
cmrcg
```

## Principal Component Analysis 

Principal Component Analysis (PCA) is a form of feature engineering that removes all of your features and replaces them with mathematical representations of their variance

```{r}
#####################################################################
# Random Forest Model with PCA and Engineering the Dependent variable
#####################################################################

########### Train/test sets##############

# set random seed
set.seed(123)
# create the training partition 70 % of total obs
inTrainingggpca <- createDataPartition(iphone_smallmatrix$iphonesentiment, p=0.7, list=FALSE)
# create training/testing dataset
gtraining <- iphone_smallmatrix[inTrainingggpca,]   
gtesting <- iphone_smallmatrix[-inTrainingggpca,]   
# verify number of obs 
nrow(gtraining)
nrow(gtesting)
########### recode the Dependent variable##############
gtraining$iphonesentiment <- recode(gtraining$iphonesentiment, '0' = 1, '1' = 1, '2' = 2, '3' = 3, '4' = 4, '5' = 4) 

gtraining$iphonesentiment <- as.factor(gtraining$iphonesentiment)

gtesting$iphonesentiment <- recode(gtesting$iphonesentiment, '0' = 1, '1' = 1, '2' = 2, '3' = 3, '4' = 4, '5' = 4) 

gtesting$iphonesentiment <- as.factor(gtesting$iphonesentiment)

str(gtraining)
### normalize and PCA ####
# data = training and testing from iphoneDF (no feature selection) 
# create object containing centered, scaled PCA components from training set
# excluded the dependent variable and set threshold to .95
preprocessParamsgpca <- preProcess(gtraining[,-59], method=c("center", "scale", "pca"), thresh = 0.95)
print(preprocessParamsgpca)

# use predict to apply pca parameters, create training, exclude dependant
gtrain.pca <- predict(preprocessParamsgpca, gtraining[,-59])

# add the dependent to training
gtrain.pca$iphonesentiment <- gtraining$iphonesentiment

# use predict to apply pca parameters, create testing, exclude dependant
gtest.pca <- predict(preprocessParamsgpca, gtesting[,-59])

# add the dependent to training
gtest.pca$iphonesentiment <- gtesting$iphonesentiment

# inspect results
str(gtrain.pca)
str(gtest.pca)

################
# Train control
################

# set 5 fold cross validation
fitControl <- trainControl(method = "cv", number = 5)

# train/fit

set.seed(123)
rf_Fitpcag<- train(iphonesentiment~., data=gtrain.pca, method="rf", trControl=fitControl, metric = "Kappa",tuneLength=5) 
rf_Fitpcag

# Save the model
saveRDS(rf_Fitpcag, "rf_Fitpcag.rds")  

# load and name model
rf_Fitpcag <- readRDS("rf_Fitpcag.rds")

#################
# Predict testSet
#################
# predict with rf
rf_Pred7g <- predict(rf_Fitpcag, gtest.pca)
rf_Pred7g

# summarize predictions
summary(rf_Pred7g)

# performance measurement
postResample(rf_Pred7g, gtest.pca$iphonesentiment)

# calculate confusion Matrix
options(max.print=10000)
cmrf <-confusionMatrix(rf_Pred7g,gtest.pca$iphonesentiment, mode="everything")
cmrf

```
# Sentiment Analysis in Large Data Matrix

## Feature Engineering

```{r}
########################################
# Feature Engineering with large matrix
########################################

# create new data set with rfe recommended features
iphone_largematrixRFE <- iphone_largematrix_N[,predictors(rfeResultsg)]

# add the dependent variable to iphoneRFE
iphone_largematrixRFE$iphonesentiment <- iphone_largematrix_N$iphonesentiment
str(iphone_largematrixRFE)
```

## Prediction

```{r}
####################
# Predict new dataSet
####################
# predict with rf
rf_Pred8g <- predict(rf_FitRCg, iphone_largematrixRFE)
rf_Pred8g
# summarize predictions
summary(rf_Pred8g)

###############
# Save datasets
###############
iphone_largematrixoutput <- iphone_largematrix
iphone_largematrixoutput$iphonesentiment<- rf_Pred8g
write.csv(iphone_largematrixoutput, file = "iphone_largematrixoutput.csv")
```

# Model Recomendation

Based on the outcomes of this modeling process, the following configuration was the most suitable in terms of quality metrics (Kappa and Accuracy).

Algorithm: Random Forest 
Feature Selection: Recursive Feature Elimination
Feature Engineering: Engineering the Dependant variable

```{r}
### Performance Metrics ###

# Modeling Metrics
ModelFitResultiphone <- resamples(list(C5.0=C5.0_Fitg,rf=rf_Fitg,SVM=svm_Fitg,kknn=kknn_Fitg,gbm=gbm_Fit3g))
# output summary metrics for tuned models 
summary(ModelFitResultiphone)

# Feature Selection
Featureselectioniphone <- resamples(list(Correlation=rf_FitCORg,NZV=grf_FitNZV,RFE=rf_FitRFEg))
# output summary metrics for feature selection 
summary(Featureselectioniphone)

# Feature Engineering 
Featureengineeringiphone <- resamples(list(DV=rf_FitRCg,PCA=rf_Fitpcag))
# output summary metrics for feature engineering
summary(Featureengineeringiphone)

stopCluster(cl)
```


End of the document 

------ SML --------
